### 2025-02-21 paper/sections/other/constraints.qmd
good starting parameters creating robust results across datasets and models

    # Counterfactuals:
    target = 2
    factual = 1
    if !any(isnothing.(x))
        yhat = [argmax(y) for y in eachcol(model(x))]
        yhat0 = [argmax(y) for y in eachcol(model(x0))]
        idx_plotted = yhat0.==factual
        if any(idx_plotted)

            # Paths:
            u = []
            v = []
            for (i,ce) in enumerate(eachcol(x))
                Δ = ce - x0[:,i]
                push!(u, Δ[1])
                push!(v, Δ[2])
            end
            Plots.quiver!(x0[1,idx_plotted], x0[2,idx_plotted], quiver=(u[idx_plotted], v[idx_plotted]), color=factual)

@@

# Data:
specs = [
    # ("(a)", VanillaObjective(needs_ce=true), ["both", "both"]),
    ("(b)", FullObjective(lambda=[1.0,0.5,0.01,1.0]), ["both", "both"]),
    # ("(c)", VanillaObjective(needs_ce=true), ["both", "none"]),
    # ("(d)", FullObjective(lambda=[1.0,1.0,0.0,1.0]), ["both", "none"]),
]
```

@@

    # Objective:
    generator = ECCoGenerator()
    opt_state = Flux.setup(Descent(), model)
    conv = DecisionThresholdConvergence(decision_threshold=0.95, max_iter=30)

>>>>

    # Counterfactuals:
    target = 2
    factual = 1
    if !any(isnothing.(x))
        yhat = [argmax(y) for y in eachcol(model(x))]
        yhat0 = [argmax(y) for y in eachcol(model(x0))]
        idx_plotted = yhat0.==factual .|| yhat0.==target
        if any(idx_plotted)

            # # Paths:
            # u = []
            # v = []
            # for (i,ce) in enumerate(eachcol(x))
            #     Δ = ce - x0[:,i]
            #     push!(u, Δ[1])
            #     push!(v, Δ[2])
            # end
            # Plots.quiver!(x0[1,idx_plotted], x0[2,idx_plotted], quiver=(u[idx_plotted], v[idx_plotted]), color=yhat0[idx_plotted])

@@

# Data:
specs = [
    # ("(a)", VanillaObjective(needs_ce=true), ["both", "both"]),
    # ("(b)", FullObjective(lambda=[1.0,0.5,0.01,0.1]), ["both", "both"]),
    # ("(c)", VanillaObjective(needs_ce=true), ["both", "none"]),
    ("(d)", FullObjective(lambda=[1.0,0.5,0.01,0.1]), ["both", "none"]),
]
```

@@

    # Objective:
    opt = AMSGrad()
    generator = GenericGenerator(opt=Descent(0.1))
    opt_state = Flux.setup(opt, model)
    conv = DecisionThresholdConvergence(decision_threshold=0.75, max_iter=30)
